\documentclass[11pt]{article}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[margin=0.5in]{geometry}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{graphicx}
\usepackage[siunitx]{circuitikz}
\usepackage{tikz}
\usepackage[colorinlistoftodos, color=orange!50]{todonotes}
\usepackage{hyperref}
\usepackage[numbers, square]{natbib}
\usepackage{fancybox}
\usepackage{epsfig}
\usepackage{soul}
\usepackage[framemethod=tikz]{mdframed}
\usetikzlibrary{positioning, automata, backgrounds}
\usepackage[shortlabels]{enumitem}
\usepackage[version=4]{mhchem}
\usepackage{multicol}
\usepackage{forest}
\usepackage{mathtools}
\usepackage{comment}
\usepackage{enumitem}
\usepackage[utf8]{inputenc}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usepackage{listings}
\usepackage{color}
\usepackage[numbers]{natbib}
\usepackage{subfiles}
\usepackage{tkz-berge}


\newcommand{\interval}[4]{\draw (#2, #1) -- (#3, #1); % Usage: \interval{height}{start}{end}{label}
\draw (#2, #1-0.11) -- (#2, #1+0.11); % draw left whisker
\draw (#3, #1-0.11) -- (#3, #1+0.11); % draw right whisker
\node[] at (#2-0.25, #1) {#4};
}

\newtheorem{prop}{Proposition}[section]
\newtheorem{thm}{Theorem}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{cor}{Corollary}[prop]

\theoremstyle{definition}
\newtheorem{definition}{Definition}

\theoremstyle{definition}
\newtheorem{required}{Problem}

\theoremstyle{definition}
\newtheorem{ex}{Example}


\setlength{\marginparwidth}{3.4cm}
%#########################################################

%To use symbols for footnotes
\renewcommand*{\thefootnote}{\fnsymbol{footnote}}
%To change footnotes back to numbers uncomment the following line
%\renewcommand*{\thefootnote}{\arabic{footnote}}

% Enable this command to adjust line spacing for inline math equations.
% \everymath{\displaystyle}

% _______ _____ _______ _      ______ 
%|__   __|_   _|__   __| |    |  ____|
%   | |    | |    | |  | |    | |__   
%   | |    | |    | |  | |    |  __|  
%   | |   _| |_   | |  | |____| |____ 
%   |_|  |_____|  |_|  |______|______|
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{
\normalfont \normalsize 
\textsc{CSCI 3104 Spring 2023 \\ 
Instructors: Ryan Layer and Chandra Kanth Nagesh} \\
[10pt] 
\rule{\linewidth}{0.5pt} \\[6pt] 
\huge Homework 6 \\
\rule{\linewidth}{2pt}  \\[10pt]
}
%\author{}
\date{}

\begin{document}

\definecolor {processblue}{cmyk}{0.96,0,0,0}
\definecolor{processred}{rgb}{200, 0, 0}
\definecolor{processgreen}{rgb}{0, 255, 0}
\DeclareGraphicsExtensions{.png}
\DeclareGraphicsExtensions{.gif}
\DeclareGraphicsExtensions{.jpg}

\maketitle


%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%FILL IN YOUR NAME%%%%%%%
%%%%%%%%%%AND STUDENT ID%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent
Due Date \dotfill February 16, 2023 \\
Name \dotfill \textbf{Blake Raphael} \\
Student ID \dotfill \textbf{109752312} \\
Collaborators \dotfill \textbf{Alex Barry and Brody Cyphers}

\tableofcontents

\section{Instructions}
 \begin{itemize}
	\item The solutions \textbf{should be typed}, using proper mathematical notation. We cannot accept hand-written solutions. \href{http://ece.uprm.edu/~caceros/latex/introduction.pdf}{Here's a short intro to \LaTeX.}
	\item You should submit your work through the \textbf{class Gradescope page} only (linked from Canvas). Please submit one PDF file, compiled using this \LaTeX \ template.
	\item You may not need a full page for your solutions; pagebreaks are there to help Gradescope automatically find where each problem is. Even if you do not attempt every problem, please submit this document with no fewer pages than the blank template (or Gradescope has issues with it).

	\item You are welcome and encouraged to collaborate with your classmates, as well as consult outside resources. You must \textbf{cite your sources in this document.} \textbf{Copying from any source is an Honor Code violation. Furthermore, all submissions must be in your own words and reflect your understanding of the material.} If there is any confusion about this policy, it is your responsibility to clarify before the due date. 

	\item Posting to \textbf{any} service including, but not limited to Chegg, Reddit, StackExchange, etc., for help on an assignment is a violation of the Honor Code.

	\item You \textbf{must} virtually sign the Honor Code (see Section \ref{HonorCode}). Failure to do so will result in your assignment not being graded.
\end{itemize}


\section{Honor Code (Make Sure to Virtually Sign)} \label{HonorCode}

%\begin{required}
\begin{itemize}
\item My submission is in my own words and reflects my understanding of the material.
\item Any collaborations and external sources have been clearly cited in this document.
\item I have not posted to external services including, but not limited to Chegg, Reddit, StackExchange, etc.
\item I have neither copied nor provided others solutions they can copy.
\end{itemize}

%\noindent In the specified region below, clearly indicate that you have upheld the Honor Code. Then type your name. 
%\end{required}

\begin{proof}[Agreed (I agree to the following, Blake Raphael).]
%% Typing "I agree to the above," followed by your name is sufficient.
\end{proof}

\newpage
\section{Standard 6 -- Safe and Useless Edges}
\setcounter{subsection}{1}
\subsection{Problem \ref{MST_Safe1} (4 points)}
\begin{required} \label{MST_Safe1}

Consider the weighted graph $G(V, E, w)$ below. Let $\mathcal{F} = \{ \{B, C\}, \{E, D\}, \{G, E\}\}$ be an intermediate spanning forest (indicated by the thick edges below). Label each edge that is \textbf {not} in $\mathcal{F}$ as safe, useless, or undecided. Provide a 1-2 sentence explanation for each such edge.


\begin{center}
\begin{tikzpicture}[scale=0.4, auto, node distance=3cm, every loop/.style={},
  thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries}]

\node[main node] (A) {A};
\node[main node] (B) [right of=A] {B};
\node[main node] (C) [above right of=B] {C};
\node[main node] (D) [below right of=C] {D};
\node[main node] (E) [below left of=D] {E};
\node[main node] (F) [below left of=E] {F};
\node[main node] (G) [above left of=F] {G};

\path[line width=0.25mm, every node/.style={font=\sffamily\small}]
(B) edge node [left]  {1} (C)
(B) edge node [left]  {5}  (E)
(C) edge node [right] {6}  (D)
(D) edge node [right] {2} (E)
(F) edge node [below] {7} (G)
(G) edge node [above] {3}  (E) 
(A) edge node [left] {4} (G)
(A) edge node [above] {10} (B)
(E) edge node [left] {8} (F)
(B) edge node [left] {9} (G)
;

\draw[line width=0.75mm] (B) -- (C);
\draw[line width=0.75mm] (E) -- (D);
\draw[line width=0.75mm] (G) -- (E);
\end{tikzpicture}
\end{center}
\end{required}

\begin{proof}[Answer]
\begin{itemize}
\item The edge $\{A,G\}$ is safe % safe/useless/undecided
because it is a minimum edge that connects without creating a cycle.\\
\item The edge $\{A, B\}$ is useless because it would create a cycle and it is not a minimum weight edge.\\
\item The edge $\{G, B\}$ is useless because it would create a cycle and it is not a minimum weight edge.\\
\item The edge $\{G, F\}$ is a safe edge because it is a minimum weight edge that doe not create a cycle.\\
\item The edge $\{F, E\}$ is a useless edge because it would create a cycle and is not a minimum weight edge.\\
\item The edge $\{E, B\}$ is a safe edge because it is a minimum weight edge that would not create a cycle.\\
\item The edge $\{C, D\}$ is a useless edge because it is not a minimum weight edge and it would create a cycle. %Your answer here
\end{itemize}
\end{proof}

\end{document} % NOTHING AFTER THIS LINE IS PART OF THE DOCUMENT
